### 2019-10-25 fe_px_paper/fe_body_text.tex
Removed Alex as co-author. Implemented all Public Utterance changes and submitted to PRC!

Developing production of these radionuclides requires well-characterized cross section data, or predictive models when such data have not been measured.   
% However, the m
Modeling of nuclear reactions in 
% this 
the A=40--70 mass region presents numerous challenges including uncertainties in nuclear level densities as a function of spin due to the opening of the $f_{7/2}$ orbital and the presence of enhanced $\gamma$-strength at low energies\,\cite{Voinov2004a,Algin2008,Algin2007}.  
% As 
Therefore, as part of a larger campaign to address deficiencies in cross-cutting nuclear data needs, our group has
% performed a   measurement of 
measured the   nuclear excitation functions of the radionuclides \ce{^{51}Mn},   \ce{^{52m}Mn}, and \ce{^{52g}Mn} from proton-induced reactions on natural iron.
% This was carried out 
% in a
% using 
We used the thin-foil stacked-target technique to study proton-induced reactions on 
% experiment, using proton irradiation of 
% natural iron foils 
iron foils of natural isotopic abundance with titanium and copper monitor foils.
% While recent work has been performed in the 40--100\,MeV energy region, t
This work 
% seeks to 
complements 
% these measurements 
earlier measurements using 40--100\,MeV protons  and extends them down to reaction thresholds,  to investigate the feasibility of production using the international network   of low-energy medical cyclotrons\,\cite{Graves2016}. 
Furthermore, 
% we are able to use a portion of the data we measured to gain insight into the role of 
we used our measured data to probe the role of angular momentum in the transitional energy region between compound and direct reactions since both the ground and long-lived isomeric states in \ce{^{52}Mn} were populated.

@@

After irradiation, all foils were 
% confirmed to 
still sealed in their Kapton packets, verifying that no activation products were lost due to packet failure.
% and dispersal.
With the exception of a single foil (Cu-20, in the 25\,MeV stack), each activated foil had a small \enquote{blister} under the Kapton tape layer, caused by a combination of 
% thermal swelling, 
off-gassing of oxides and the formation of gaseous short-lived beta activities in the tape.
% \comment{Maybe some Ne formed by Al(p,2a)Ne / Si(p,2ap)Ne?}
This blister   verifies that the primary proton beam was incident upon the foil, and provides additional 
% the first 
evidence 
% (before gamma-ray spectrometry) 
that the beam was stopped in the stack between Ti-20 and Cu-20.
% , producing a Bragg peak at this location.  
Using the \ce{^{nat}Ti}(p,x)\ce{^{46}Sc}, \ce{^{nat}Ti}(p,x)\ce{^{48}V}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{63}Zn} monitor reactions, as discussed in \autoref{sec:proton_transport_fe}, a fluence of 17.9$~\pm~$1.0\,nAh 
% 18.8$\pm$1.0\,nAh
was calculated to be incident upon the 55\,MeV target stack using the FLUKA fluence model, and a  fluence of 19.0$~\pm~$1.3\,nAh using the linear fit model.
Similarly, for the 25\,MeV stack, a fluence of 27.5$~\pm~$8.3\,nAh 
% 33.2$\pm$4.7\,nAh
was calculated to be incident upon the 
% 55\,MeV 
target stack using the FLUKA fluence model, and a  fluence of 31.7$~\pm~$3.7\,nAh using the linear fit model to the four frontmost compartments (before the fluence loss becomes strongly nonlinear).
% 37.0$\pm$9.3\,nAh using the linear fit model.
% All of these 
Both linear models are consistent with the nominal fluence of 20.78\,nAh (for the 55\,MeV stack) and 31.61\,nAh (for the 25\,MeV stack) measured using the 
% beamline 
current integrators.
However, for both target stacks, the FLUKA transport model predicts a significant increase in proton fluence, in particular for the 25\,MeV stack.
This model fails to reproduce the fluence loss seen in monitor foils, and predicts a significantly higher production of secondary protons not seen in the activation data.
As fluence loss scales with $\sigma_{\mathrm{tot}}\rho\Delta r$, it is expected that an extrapolation back to the stack entrance (through the SS-3/SS-5 profile monitors) will underestimate the nominal fluence incident upon the box.
This incident fluence dropped by approximately 
% 9.5\% to  17.0$\pm$2.4\,nAh (and by 
8.9\% to  17.3$~\pm~$1.5\,nAh using the linear fit model over the length of the 55\,MeV stack, which is consistent with similar measurements at the Los Alamos National Laboratory's Isotope Production Facility in the past\,\cite{Voyles2018a,Graves2016}.
This loss of fluence is due to a combination of 
% beam utilization for the various 
(p,x) reactions throughout the target stack, as well as large-angle deflections (primarily in the aluminum degraders) from scattering of the beam.

>>>>

Developing production of these radionuclides requires well-characterized cross section data, or predictive models when such data have not been measured.   
% However, the m
Modeling of nuclear reactions in 
% this 
the A=40--70 mass region presents numerous challenges including uncertainties in nuclear level densities as a function of spin due to the opening of the $f_{7/2}$ orbital and the presence of enhanced $\gamma$-strength at low energies\,\cite{Voinov2004a,Algin2008,Algin2007}.  
% As 
Therefore, as part of a larger campaign to address deficiencies in cross-cutting nuclear data needs, our group has
% performed a   measurement of 
measured the   nuclear excitation functions of the radionuclides \ce{^{51}Mn},   \ce{^{52m}Mn}, and \ce{^{52g}Mn} from proton-induced reactions on Fe.
% natural iron.
% This was carried out 
% in a
% using 
We used the thin-foil stacked-target technique to study proton-induced reactions on 
% experiment, using proton irradiation of 
% natural iron foils 
% iron 
Fe foils of natural isotopic abundance with 
% titanium 
Ti and 
% copper 
Cu monitor foils.
% While recent work has been performed in the 40--100\,MeV energy region, t
This work 
% seeks to 
complements 
% these measurements 
earlier measurements using 40--100\,MeV protons  and extends them down to reaction thresholds,  to investigate the feasibility of production using the international network   of low-energy medical cyclotrons\,\cite{Graves2016}. 
Furthermore, 
% we are able to use a portion of the data we measured to gain insight into the role of 
we used our measured data to probe the role of angular momentum in the transitional energy region between compound and direct reactions since both the ground and long-lived isomeric states in \ce{^{52}Mn} were populated.

@@

After irradiation, all foils were 
% confirmed to 
still sealed in their Kapton packets, verifying that no activation products were lost due to packet failure.
% and dispersal.
With the exception of a single foil (Cu-20, in the 25\,MeV stack), each activated foil had a small \enquote{blister} under the Kapton tape layer, caused by a combination of 
% thermal swelling, 
off-gassing of oxides and the formation of gaseous short-lived beta activities in the tape.
% \comment{Maybe some Ne formed by Al(p,2a)Ne / Si(p,2ap)Ne?}
This blister   verifies that the primary proton beam was incident upon the foil, and provides additional 
% the first 
evidence 
% (before gamma-ray spectrometry) 
that the beam was stopped in the stack between Ti-20 and Cu-20.
% , producing a Bragg peak at this location.  
Using the \ce{^{nat}Ti}(p,x)\ce{^{46}Sc}, \ce{^{nat}Ti}(p,x)\ce{^{48}V}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{63}Zn} monitor reactions, as discussed in \autoref{sec:proton_transport_fe}, a fluence of 17.9$~\pm~$1.0\,nAh 
% 18.8$\pm$1.0\,nAh
was calculated to be incident upon the 55\,MeV target stack using the FLUKA fluence model, and a  fluence of 19.0$~\pm~$1.3\,nAh using the linear fit model.
Similarly, for the 25\,MeV stack, a fluence of 27.5$~\pm~$8.3\,nAh 
% 33.2$\pm$4.7\,nAh
was calculated to be incident upon the 
% 55\,MeV 
target stack using the FLUKA fluence model, and a  fluence of 31.7$~\pm~$3.7\,nAh using the linear fit model to the four frontmost compartments (before the fluence loss becomes strongly nonlinear).
% 37.0$\pm$9.3\,nAh using the linear fit model.
% All of these 
Both linear models are consistent with the nominal fluence of 20.78\,nAh (for the 55\,MeV stack) and 31.61\,nAh (for the 25\,MeV stack) measured using the 
% beamline 
current integrators.
However, for both target stacks, the FLUKA transport model predicts a significant increase in proton fluence, in particular for the 25\,MeV stack.
This model fails to reproduce the fluence loss seen in monitor foils, and predicts a significantly higher production of lower-energy secondary protons not seen in the activation data.
As fluence loss scales with $\sigma_{\mathrm{tot}}\rho\Delta r$, it is expected that an extrapolation back to the stack entrance (through the SS-3/SS-5 profile monitors) will underestimate the nominal fluence incident upon the box.
This incident fluence dropped by approximately 
% 9.5\% to  17.0$\pm$2.4\,nAh (and by 
8.9\% to  17.3$~\pm~$1.5\,nAh using the linear fit model over the length of the 55\,MeV stack, which is consistent with similar measurements at the Los Alamos National Laboratory's Isotope Production Facility in the past\,\cite{Voyles2018a,Graves2016}.
This loss of fluence is due to a combination of 
% beam utilization for the various 
(p,x) reactions throughout the target stack, as well as large-angle deflections (primarily in the aluminum degraders) from scattering of the beam.
